Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-27 src/article.tex
abstract versions

@@

% Several key features were implemented to address the project’s requirements:

% \begin{itemize}
% \item \emph{QRE1113 infrared sensors}. These sensors were selected for their non-invasive properties and precision, enabling the detection of jack displacement without requiring structural modifications to the keyboard mechanism.
% \item \emph{Gradient stickers}. Greyscale gradient stickers were applied to each jack to allow the infrared sensors to make precise readings. This approach made calibration easier and enabled scalability from a 3-key prototype to the final 49-key design.
% \item \emph{Jack baffles}. Custom-designed baffles, 3D printed from dark pigmented PLA to minimise infrared reflection, were installed around the jacks to prevent cross-talk between adjacent sensors and ensure reliable data capture.
% \end{itemize}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{src/images/49-key-bottom-sensors-no-keys.jpg} 
  \caption{Underside of the full model keyboard, showing two chambers: the front chamber (top) and the rear chamber (bottom).} 
  \Description{} 
  \label{fig:49-key-bottom}
\end{figure}

@@

Reference repositories for this project can be found here:
\begin{anonsuppress}
    \begin{itemize}
        \item 
        \emph{Firmware}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-firmware}}
        \item 
        \emph{PCB CAD}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-cad}}
        \item 
        \emph{Interface Models}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-models}}
    \end{itemize}
\end{anonsuppress}
% FILL OUT AS APPROPRIATE (and anonymise).

>>>>

\begin{figure}[b]
  \centering
  \includegraphics[width=\linewidth]{src/images/49-key-bottom-sensors-no-keys.jpg} 
  \caption{Underside of the full model keyboard, showing two chambers: the front chamber (top) and the rear chamber (bottom).} 
  \Description{} 
  \label{fig:49-key-bottom}
\end{figure}

@@

\subsubsection{Alternative}
\textcolor{red}{The final design, visible in Figures \ref{fig:teaser} and \ref{fig:details}, is a 49-key two-register harpsichord keyboard replica.
The keyboard was consciously chosen to mimic that of the original XVI century Italian harpsichords. This design decision was made in order to use the propensity humans have to being influenced by visual components when musical making judgements \cite{Tsay2013} to our advantage. It is especially true with respect to musical instruments as the studies by Fritz \emph{et al}\cite{Fritz2012, Fritz2014, Fritz2017} have clearly shown. Rather than avoiding this effect we have chosen to instead utilise it. This `musical instrument McGurk effect' is in part the reason behind hiding the electronics out of sight. 
The aesthetics of the interface make it more likely that the interface be accepted on the same terms as an `authentic' musical instrument. With all the work into modelling and recreating piano action \cite{Cadoz1990, Gillespie1996, Timmermans2020} it is possible the visual component my provide the necessary push of acceptance similar to that which influences our judgment on performance \cite{Tsay2013}. 
Such an effect is invaluable if visitors are expected to engage with the interface on an equal footing as the historic instruments that neighbour it in the museum.
The keyboard in not merely a facsimile of a harpsichord, but rather by being equipped with optical sensors, it can provide modes of expression with a digital instrument which would otherwise be inaccessible to its analogue sibling. 
The optical sensors are wired in a voltage divider configuration (Figure \ref{fig:simple-schematic}) whose voltage output depends on the amount of light reflected by sensor surface. In this case, a sensor surface is a grey-scale gradient printed on a vinyl sticker and applied to the side of each jack (Figure \ref{fig:jack-tags}). Though the current configuration simply sends MIDI note on and off at passing a threshold, the displacement of all jacks is available continuously. Touch with the key
The double register means that there are two very distinct tactile `anchors' in the course of the keys travel that is championed by professional harpsichordists as invaluable vector for expression during performance.  (GOING TO NEED A REFERENCE ON THIS BUT FAIRLY CONFIDENT I SAW IT IN THE TAGLIAVINI BOOK. MICHELE IF YOU HAVE A REFERENCE LEAVE IT HERE).}
% "When working with an established interface like the keyboard, it is particularly important that new mappings do not interfere with familiar technique (McPherson, Gierakowski, and Stark 2013)."

@@

@@

\begin{anonsuppress}
Reference repositories for this project can be found here:

    \begin{itemize}
        \item 
        \emph{Firmware}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-firmware}}
        \item 
        \emph{PCB CAD}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-cad}}
        \item 
        \emph{Interface Models}: \anon{\url{https://github.com/Nemus-Project/haprsichord-interface-models}}
    \end{itemize}
\end{anonsuppress}
% FILL OUT AS APPROPRIATE (and anonymise).
